Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-01 Scripts/Initial_Analysis.Rmd
sip fig 1

@@

@@

# time <- "per_mid_plot"
time <- "per_early"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
           aes(start_lon,
               start_lat,
               col = per_plot),
           size = 0.05,
           col = "gray80",
           shape = 20,
           stroke = 1.5) +
geom_path(data = subset(paths, time_step == time & per_plot > 0),
          aes(X,
              Y,
              group = interaction(line_id,subline_id),
              col = per_plot
          ),
          size = 0.3,
          lineend = "round",
          arrow = arrow(length = unit(0.008, "npc"),
                        ends = "first"),
          show.legend = NA) +
  my_ggtheme_m() +
scale_colour_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # option="magma",
  # direction = -1
) +
scale_fill_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # alpha = 0.8
  # option="magma",
  # direction = -1
) +
ggsave("./Figures/fig2ax.png",
       width = 12,
       height = 8,
       units = "in"
)

@@

@@

# -------------------------------- #
#### Prepare data
# -------------------------------- #

Lm_data <- Eme_Res %>% # 19728
  filter(tresh == "Tresh_one") %>% # 11490
  left_join(Spp_depth) %>% 
  select(taxon_key,tresh,sf_eez_name,sau_fishing_entity,fishing_entity_id,emerging_yr,eezid,dem_pel,un_region= un_geo_region) %>% 
  left_join(Toe_temp,
            by = c("eezid","tresh")
            ) %>% 
  left_join(Catch_trend,
            by = c("taxon_key","sau_fishing_entity","fishing_entity_id")
            ) %>% # 11492
  left_join(Eez_biogeo,
            by = "eezid") %>% 
  left_join(Spp_env_pref,
            by = "taxon_key") %>% 
  left_join(Eez_centroids,
            by = "eezid") %>% 
  mutate(latitude = abs(latitude))

>>>>

Main_data <- Eme_Res %>% # 19728
  filter(tresh == "Tresh_one") %>% # 11490
  left_join(Spp_depth) %>% 
  select(taxon_key,tresh,sf_eez_name,sau_fishing_entity,fishing_entity_id,emerging_yr,eezid,dem_pel,un_region= un_geo_region) %>% 
  left_join(Toe_temp,
            by = c("eezid","tresh")
            ) %>% 
  left_join(Catch_trend,
            by = c("taxon_key","sau_fishing_entity","fishing_entity_id")
            ) %>% # 11492
  left_join(Eez_biogeo,
            by = "eezid") %>% 
  left_join(Spp_env_pref,
            by = "taxon_key") %>% 
  left_join(Eez_centroids,
            by = "eezid") %>% 
  mutate(latitude = abs(latitude))

@@

### Median number

Prop_results %>% 
  filter(variable == "n_spp") %>% 
  group_by() %>% 
  summarise(
    median(early,na.rm=T),
    sd(early,na.rm=T)
  )

@@

time <- "per_mid"
# time <- "per_early"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
           aes(start_lon,
               start_lat,
               col = per_plot),
           size = 0.05,
           col = "gray80",
           shape = 20,
           stroke = 1.5) +
geom_path(data = subset(paths, time_step == time & per_plot > 0),
          aes(X,
              Y,
              group = interaction(line_id,subline_id),
              col = per_plot
          ),
          size = 0.3,
          lineend = "round",
          arrow = arrow(length = unit(0.008, "npc"),
                        ends = "first"),
          show.legend = NA) +
  my_ggtheme_m() +
scale_colour_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # option="magma",
  # direction = -1
) +
scale_fill_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # alpha = 0.8
  # option="magma",
  # direction = -1
) +
ggsave("./Figures/fig_sup_1.png",
       width = 12,
       height = 8,
       units = "in"
)

@@

## Top fishing nations
Buble_data %>% 
  filter(log_value > Percentile_value$x) %>% 
  View()

@@
